Background for transient faults in asynchronous circuits

### 2019-04-17 draft_together3.tex
edited proofs a bit

\begin{lemma}[1]
If $\sigma$ is the trace of the fault tolerant circuit and the A half is fault free, then in the A half:
\begin{itemize}
\item  $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit, regardless of the wire values in the B half.
\item the logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
\item For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ in the fault tolerant circuit.  (No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)  A wire $w$ in $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault tolerant circuit.
\end{itemize}

@@

%If the duplicated circuit is in state $s_n$ and the original circuit is in state $h^A(s_n)$, and for all wires $w$ that are excited in this state $f_w(s_n|_I)\neq w$ in original circuit, then $f_w(s_n|_I) \neq x^A$ or $x^A \neq w^A$ in duplicated circuit (exactly one of these is true).  
%In addition, if wire $w$ is not excited in the original circuit $f_w(s_n|_I)=w$, then in the duplicated circuit half $f_w(s_n|_I)=x^A=w^A$.  
\end{lemma}
The trace $\sigma$ can be finite or infinite in length in accordance with the definition of a trace. 
\begin{proof}
We prove this Lemma by induction on all traces of the circuit of length $n$.  The induction hypothesis is:
\begin{itemize}
\item Assume that $\sigma$ is a trace in the fault tolerant circuit.  Then $\sigma_n$ maps to $h^{A}(\sigma_n)$, which is a prefix of a trace of the original circuit.
\item Every logic block is in a semi-modularity consistent state.  %newly added, a new property outside of \sigma_n mapping to h^A(\sigma_n)
\item In every state $s$ of $\sigma_n$, it is true that a wire $w$ in the original circuit of state $h^A(s)$ is excited if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ (the new value is propagating down one of the logic block or chain of C-elements).  The case where two or more of the three conditions being true does not exist in this setting.  Also a wire $w$ is unexcited if and only if none of the four excited conditions are true. \\
%Proving any two of the above three statements is equivalent to the third being true as well.% also I'm calling h^A(s_k) to mean the unduplicated circuit with these states assigned.... forget if I explained or not
\end{itemize}
% true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
We show in the base case that the induction hypotheses hold for any state in the fault tolerant circuit constructed from a valid initial state (ie. all possible traces of length 1). 
\begin{itemize}
\item For every $s_1$ that is a valid initial state we have that $h^A(s_1)$ is some state in the original circuit by its construction.  Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit.  
\item We assigned the wire values so that the logic blocks are in a semi-modularity consistent state.  
\item For any wire $w$, since the input wire values are identical in the original circuit and in the A half and $c1^A=w$ then $c1^A$ is excited if and only if $w$ is excited in the original circuit.  This case can also interpreted as the logic block being excited.  Additionally there are no excitations within the C-element chain because in the valid initial state assignment $c1^A=c2^A=c3^A=w^A$.  As a result, $w$ is excited in $h^A(s_k)$ if $c1^A$ is excited in the A half.  By similar logic, for unexcited wires in the original circuit, the corresponding $c1^A$ is not excited and $c1^A=c2^A=c3^A=w^A$ from the initial assignment.  This shows the valid initial state also satisfies the last part of the induction hypothesis.    %is this enough.... that the existing states follow that iff statement?
\end{itemize}

The induction step is to assume that the induction hypotheses is true for $\sigma_k$, the subsequence for a trace $\sigma$ with length greater than or equal to $k$.  We will prove that the induction hypothesis is also true for $\sigma_{k+1}$, if it exists.  In particular for all possible $s_{k+1}$ we show that either $h^A(s_{k})=h^A(s_{k+1})$ or $T(h^A(s_{k}),h^A(s_{k+1}))$ to satisfy the first induction hypothesis.  Then we show that for all possible $s_{k+1}$ logic block remains in a semi-modularity consistent state.  Finally for all wires in $s_{k+1}$, the third induction hypothesis is true.\\

From state $s_k$, we look at all possible transitions; a transition may only occur on excited gates or c-elements.  If the transition occurs on the other half then no wire values changed in the A-half and the induction hypothesis remain true.  Thus we only need to consider the wires $w$ which are excited in the original circuit in state $h^A(s_k)$ and its corresponding wires in the A-half circuit.  For each excited wire $w$, the last induction hypothesis narrows the possible wires that can be excited in state $s_k$ and we examine the properties of the next state for each transition that can occur.  Refer to figure \ref{fig:l1helper} for an example of what happens in each of the cases.  These are drawn for when $w$ transitions from $0\rightarrow1$ but the transition from $1\rightarrow0$ can also be visualized with the same figure by inverting 1's and 0's. %logic gate excited = c1^A excited
%possibly add graph to illustrate this
\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{gatewl1}
  \caption{Different cases of the induction step for proving Lemma 1.  a) case 1, b) case 2, c) case 3, d) case 4}
  \label{fig:l1helper}
\end{figure}

\begin{itemize}
\item The first case is for an excited wire $w$.  The corresponding $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.  Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, thus wire $w$ satisfies the third induction hypothesis.  Since the transition occurred on an intermediate wire, the set of excited wires in state $h^A(s_{k+1})$ of the original circuit does not change and for both excited wires $v$ where $v\neq w$ and not excited wires the third induction hypothesis carries over from $s_k$ to $s_{k+1}$.  Thus the third induction hypothesis is true for all output wires.  Also since the output wires did not change, then $h^A(s_k)=h^A(s_{k+1})$ satisfying the first induction hypothesis.  The output wires not changing also allow the logic blocks to stay in a semi-modularity consistent state.   The induction hypotheses are true for any transition from this case.  %don't know if this needs to be explained more (and add that the non-excited wires are still non-excited?)
%since the inputs to the gate and the intermediate wires did not transition, then the gate is excited or $y^{A,B}\neq v^{A,B}$.  
%do I need to show that non-excited has nothing excited in duplicated
%$w$ is still excited in $h^A(s_{k+1})$ and in state $s_{k+1}$ only $c1^{A}\neq c2^{A}$ is true.   Therefore in this case the property is true for state $s_{k+1}$
\item The second case is when the signal propagates down to $c2^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c1^A=c2^A$ and $c2^{A}\neq c3^{A}$ and thus wire $w$ satisfies the third induction hypothesis.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.   
\item The third case is similar to the second case and occurs when the signal propagates down to $c3^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A$, $c2^{A}\neq c3^{A}$ and $c3^A=w^A$, then $c3^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c2^A=c3^A$ and $c3^{A}\neq w^{A}$ and thus wire $w$ satisfies the third induction hypothesis.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.

\item The fourth case is when the signal propagates down to $w^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A=c3^A$ and $c3^A\neq w^A$, then $w^A$ transitions.  Since $w$ is excited in $h^A(s_k)$, then $T(h^A(s_k), h^A(s_{k+1}))$ which satisfies the first induction hypothesis.  Also since $h^A(s_{k+1})$ is a state in the original semi-modular circuit and the A-half logic blocks at state $s_k$ are semi-modularity consistent, inputs to all logic blocks in the A-half are also semi-modularity consistent. Then we look at the third induction hypothesis by partitioning all of the wires into 4 subcases: the transitioning wire $w$; excited wires in state $h^A(s_k)$ other than $w$; newly excited wires in state $h^A(s_{k+1})$; and wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$.  (excited wires in $h^A(s_k)$ cannot be unexcited in $h^A(s_{k+1})$ by the semi-modularity property)  
\begin{itemize}
\item
$w$ is unexcited in state $h^A(s_{k+1})$ (we disregard the possibility that w can be immediately excited again), and in the A-half the changes are that $c3^{A}= w^{A}$.  Thus $w$ is unexcited and also the corresponding wires in the fault tolerant circuit are unexcited, wire $w$ satisfies the third induction hypothesis.  
\item
For any excited wire $v$ in state $h^A(s_k)$ and $v\neq w$, by semi-modularity of the original circuit $v$ is excited in state $h^A(s_{k+1})$ as well.  Thus, $c1^A$ of $v$ will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, wires of this type satisfy the third induction hypothesis.  
\item
For all newly excited wires $u$ in $h^A(s_{k+1})$, then in state $s_{k}$ $u$ is not excited in $h^A(s_k)$ and $c1^A=c2^A=c3^A=u^A=u$ and this is true in $s_{k+1}$ as well.  But since $u$ is excited then $c1^A$ in the A half must be excited.  Thus wires of this type satisfy the third induction hypothesis. 
\item
Finally for all other wires, ones that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, the logic gate is not excited and $c1^A=c2^A=c3^A=u^A$.  Thus wires of this type satisfy the third induction hypothesis.  
\end{itemize}
Then the induction hypotheses are true for any transition from this case. 
\end{itemize}
So the induction hypotheses holds for all possible $\sigma_{k+1}$ and the induction step is complete. \\
By induction on the length of the trace, the first property shows that $h^{A,B}(\sigma_n)$ is the prefix of a trace from the original circuit for all n.
%do I need to show the opposite?  At every step the previous transitions are possible??  Dunno if true for faults though.... also something about collapsed states can't tell the difference?  Can we just map it to a circuit where everything goes together? <- this needs proving?

@@

Note as described previously that the proof for Lemma 1 does not place any restrictions on the other half of the circuit other than that it does not break the digital abstraction for the C-elements that has inputs from both halves of the circuit (e.g. does not cause hazards in the C-element output).  Thus this Lemma is true regardless of whether there is a fault or not in the other half of the circuit.  It guarantees that if there is a next state it must follow the state transitions of the original circuit, but does not guarantee that there will be a next state.\\  %maybe move this to in front of L1

@@

We look at the base case for every wire $w$ in the original circuit.  Because the duplicated circuit starts at the same valid initial state: $w=c1^A=c2^A=c3^A=w^A=c1^B=c2^B=c3^B=w^B$.  A wire $w$ can be either excited or unexcited in the original circuit. If the wire $w$ is unexcited, applying Lemma 1,  A and B halves of $w$ in the duplicated circuit are in case 1 (or case 11, we will here on ignore the inverted 1's and 0's states, but each case technically represents two states).  If $w$ is excited then Lemma 1 states that the logic blocks must be excited, which is case 2.  Thus this property is true for the base case. \\

@@

For all possible transitions from $s_k$, we verify that each $s_{k+1}$ has wire blocks that is in one of the cases in figure \ref{fig:l21}.  It is clear that the arrows represent transitions and logic block changes that can occur, thus we are verifying that there does not exist additional cases a transition can lead to, namely that the logic blocks does not behave inappropriately since the wires in the C-element chains behave as the arrows indicate.  Because the arrows do not always indicate wire transitions (some are transitions between excited or unexcited state of the logic blocks which are in response to transitions of other wires), we only need to verify that for the transitions that do occur (black arrows), it does not cause the other logic blocks to behave inappropriately.

@@

Cases 9/10a/10b:  In cases 1-8a/8b all transitions happen on intermediate wires so the state of the other wire blocks must remain the same.  In cases 9/10a/10b an output/input wire is changed so we must also consider the effects on the other wire blocks.  In case 9, when $w^a$ or $w^b$ is excited and transitions to 10a or 10b, an output wire is changed.  If any logic blocks are in case 9, its logic block cannot change excitations because it would violate Lemma 1.  Thus far, we have shown why the logic blocks in cases 1-9 cannot change excitations other than when drawn in the figure.  The last step is to show that the logic blocks in case 10a or 10b also cannot change excitations.  \\  

>>>>

\begin{lemma}[1]
If $\sigma$ is the trace of the fault tolerant circuit and the A half is fault free, then in the A half:
\begin{itemize}
\item  $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit, regardless of the wire values in the B half.
\item the logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
\item For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true in the fault tolerant circuit: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.  (No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)  A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault tolerant circuit.
\end{itemize}

@@

%If the duplicated circuit is in state $s_n$ and the original circuit is in state $h^A(s_n)$, and for all wires $w$ that are excited in this state $f_w(s_n|_I)\neq w$ in original circuit, then $f_w(s_n|_I) \neq x^A$ or $x^A \neq w^A$ in duplicated circuit (exactly one of these is true).  
%In addition, if wire $w$ is not excited in the original circuit $f_w(s_n|_I)=w$, then in the duplicated circuit half $f_w(s_n|_I)=x^A=w^A$.  
\end{lemma}
The trace $\sigma$ can be finite or infinite in length in accordance with the definition of a trace. 
\begin{proof}
We prove this lemma by induction on all traces of length $n$.  The induction hypothesis is the same as the items in the definition of the lemma but for traces of length $n$:
\begin{itemize}
\item Assume that $\sigma$ is a trace in the fault tolerant circuit.  Then $\sigma_n$, the first n states of the trace, maps to $h^{A}(\sigma_n)$, which is a prefix of a trace of the original circuit.
\item Every logic block is in a semi-modularity consistent state.  %newly added, a new property outside of \sigma_n mapping to h^A(\sigma_n)
\item In every state $s$ of $\sigma_n$, a wire $w$ in state $h^A(s)$ is excited in the original circuit is excited if and only if exactly one of the following is true in the fault tolerant circuit: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ (the new value is propagating down one of the logic block or chain of C-elements).  No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.  A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault tolerant circuit.\\
%Proving any two of the above three statements is equivalent to the third being true as well.% also I'm calling h^A(s_k) to mean the unduplicated circuit with these states assigned.... forget if I explained or not
\end{itemize}
% true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
We show in the base case that the induction hypotheses hold for any state in the fault tolerant circuit constructed from a valid initial state (ie. all possible traces of length 1). 
\begin{itemize}
\item For every $s_1$ that is a valid initial state, we have that $h^A(s_1)$ is some state in the original circuit by construction.  Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit.  
\item We assigned the initial wire values so that the logic blocks are in a semi-modularity consistent state.  
\item For any wire $w$, since the input wire values are identical in the original circuit and in the A half, both $c1^A$ and $w$ are outputs of logic blocks in the same topology and $c1^A=w$, then $c1^A$ is excited if and only if $w$ is excited in the original circuit.  This case can also be interpreted as the logic blocks in their respective circuits being excited.  Additionally there are no excitations within the C-element chain of the fault tolerant circuit because the valid initial state assigns $c1^A=c2^A=c3^A=w^A$.  As a result, $w$ is excited in $h^A(s_k)$ if $c1^A$ is excited in the A half.  By similar logic, for unexcited wires in the original circuit, the corresponding $c1^A$ is not excited and $c1^A=c2^A=c3^A=w^A$ from the initial assignment.  This shows the valid initial state also satisfies the last part of the induction hypothesis.    %is this enough.... that the existing states follow that iff statement?
\end{itemize}

The induction step is to assume that the induction hypotheses is true for $\sigma_k$, the first $k$ states of a trace $\sigma$ with length greater than or equal to $k$.  We will prove that the induction hypothesis is also true for $\sigma_{k+1}$, if it exists.  In particular for all possible $s_{k+1}$ we show that either $h^A(s_{k})=h^A(s_{k+1})$ or $T(h^A(s_{k}),h^A(s_{k+1}))$ to satisfy the first induction hypothesis.  Then we show that for all possible $s_{k+1}$ logic block remains in a semi-modularity consistent state.  Finally for all wires in $s_{k+1}$, the third induction hypothesis is true.\\

From state $s_k$, we look at all possible transitions; a transition may only occur on excited gates or c-elements.  If the transition occurs on the B-half then no wire values changed in the A-half and the induction hypothesis remain true.  Thus we only need to consider the wires $w$ which are excited in the original circuit in state $h^A(s_k)$ and its corresponding wires in the A-half circuit.  For each excited wire $w$, the last induction hypothesis narrows the possible wires that can be excited in state $s_k$ and we examine the properties of the next state for each transition that can occur.  Refer to figure \ref{fig:l1helper} for an example of what happens in each of the cases.  These are drawn for when $w$ transitions from $0\rightarrow1$, but the transition from $1\rightarrow0$ can also be visualized with the same figure by inverting the 1's and 0's. %logic gate excited = c1^A excited
%possibly add graph to illustrate this
\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{gatewl1}
  \caption{Different cases of the induction step for proving Lemma 1.  a) case 1, b) case 2, c) case 3, d) case 4}
  \label{fig:l1helper}
\end{figure}

\begin{itemize}
\item The first case is for an excited wire $w$.  In the fault tolerant circuit, wire $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.  Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, thus wire $w$ satisfies the third induction hypothesis.  Since the transition occurred on an intermediate wire, the set of excited wires in state $h^A(s_{k+1})$ of the original circuit does not change and for both excited wires $v$ where $v\neq w$ and unexcited wires, the third induction hypothesis carries over from $s_k$ to $s_{k+1}$.  Thus the third induction hypothesis is true for all output wires.  Also since the output wires did not change, then $h^A(s_k)=h^A(s_{k+1})$ satisfying the first induction hypothesis.  The output wires not changing also allow the logic blocks to stay in a semi-modularity consistent state.   The induction hypotheses are true for any transition from this case.  %don't know if this needs to be explained more (and add that the non-excited wires are still non-excited?)
%since the inputs to the gate and the intermediate wires did not transition, then the gate is excited or $y^{A,B}\neq v^{A,B}$.  
%do I need to show that non-excited has nothing excited in duplicated
%$w$ is still excited in $h^A(s_{k+1})$ and in state $s_{k+1}$ only $c1^{A}\neq c2^{A}$ is true.   Therefore in this case the property is true for state $s_{k+1}$
\item The second case is when the signal propagates down to $c2^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c1^A=c2^A$ and $c2^{A}\neq c3^{A}$ and thus wire $w$ satisfies the third induction hypothesis.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.   
\item The third case is similar to the second case and occurs when the signal propagates down to $c3^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A$, $c2^{A}\neq c3^{A}$ and $c3^A=w^A$, then $c3^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c2^A=c3^A$ and $c3^{A}\neq w^{A}$ and thus wire $w$ satisfies the third induction hypothesis.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.

\item The fourth case is when the signal propagates down to $w^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A=c3^A$ and $c3^A\neq w^A$, then $w^A$ transitions.  Since $w$ is excited in $h^A(s_k)$, then $T(h^A(s_k), h^A(s_{k+1}))$ which satisfies the first induction hypothesis.  Also since $h^A(s_{k+1})$ is a state in the original semi-modular circuit and the A-half logic blocks at state $s_k$ are semi-modularity consistent, inputs to all logic blocks in the A-half are also semi-modularity consistent. Then we look at the third induction hypothesis by partitioning all of the wires into 4 subcases: the transitioning wire $w$; excited wires in state $h^A(s_k)$ other than $w$; newly excited wires in state $h^A(s_{k+1})$; and wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$.  (excited wires in $h^A(s_k)$ cannot be unexcited in $h^A(s_{k+1})$ by the semi-modularity property)  
\begin{itemize}
\item
The wire $w$ is unexcited in state $h^A(s_{k+1})$ (we disregard the possibility that w can be immediately excited again), and in the A-half circuit, $w^A$ transitions so that $c3^{A}= w^{A}$.  So both $w$ is unexcited and the corresponding wires in the fault tolerant circuit are unexcited, thus wire $w$ satisfies the third induction hypothesis.  
\item
For any excited wire $v$ in state $h^A(s_k)$ and $v\neq w$, by semi-modularity of the original circuit $v$ is excited in state $h^A(s_{k+1})$ as well.  Thus, $c1^A$ of $v$ will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, wires of this type satisfy the third induction hypothesis.  
\item
For all newly excited wires $u$ in $h^A(s_{k+1})$, then in state $s_{k}$ $u$ is not excited in $h^A(s_k)$ and $c1^A=c2^A=c3^A=u^A=u$ and this is true in $s_{k+1}$ as well.  But since $u$ is excited then $c1^A$ in the A half must be excited.  Thus wires of this type satisfy the third induction hypothesis. 
\item
Finally for all other wires, ones that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, the logic gate is not excited and $c1^A=c2^A=c3^A=u^A$.  Thus wires of this type satisfy the third induction hypothesis.  
\end{itemize}
Then the induction hypotheses are true for any transition from this case. 
\end{itemize}
So the induction hypotheses holds for all possible $\sigma_{k+1}$ and the induction step is complete. \\
By induction on the length of the trace, the first property shows that $h^{A,B}(\sigma_n)$ is the prefix of a trace from the original circuit for all n.
%do I need to show the opposite?  At every step the previous transitions are possible??  Dunno if true for faults though.... also something about collapsed states can't tell the difference?  Can we just map it to a circuit where everything goes together? <- this needs proving?

@@

Note as described previously, the proof for Lemma 1 does not place any restrictions on the other half of the circuit other than that the digital abstraction is not violated for C-elements with inputs from both halves of the circuit (e.g. does not cause hazards in the C-element output).  Thus this lemma is true regardless of whether there is a fault or not in the other half of the circuit.  It guarantees that if there is a next state it must follow the state transitions of the original circuit, but does not guarantee that there will be a next state.\\  %maybe move this to in front of L1

@@

We look at the base case for every wire $w$ in the original circuit.  In the fault tolerant circuit, the valid initial state initializes the wires to: $w=c1^A=c2^A=c3^A=w^A=c1^B=c2^B=c3^B=w^B$.  A wire $w$ can be either excited or unexcited in the original circuit. If the wire $w$ is unexcited, applying Lemma 1,  A and B halves of $w$ in the duplicated circuit are in case 1 (or case 11, we will here on ignore the inverted 1's and 0's states, but each case technically represents two states).  If $w$ is excited then Lemma 1 states that the logic blocks must be excited, which is case 2.  Thus this property is true for the base case. \\

@@

For all possible transitions from $s_k$, we verify that each $s_{k+1}$ has wire blocks that is in one of the cases in figure \ref{fig:l21}.  It is clear that the arrows represent transitions and logic block changes that can occur.  We can also easily verify that the wires in the C-element chains behave only as the arrows indicate, thus we need to show that additional changes due to the logic blocks cannot occur.  Because the arrows do not always indicate wire transitions (some are transitions between excited or unexcited state of the logic blocks which are in response to transitions of other wires), we need only to verify for the transitions that do occur (black arrows), it does not cause the other logic blocks to behave inappropriately.

@@

Cases 9/10a/10b:  In cases 1-8a/8b all transitions happen on intermediate wires so the state of the other wire blocks must remain the same.  In cases 9/10a/10b an output/input wire is changed so we must also consider the effects on the other wire blocks.  In case 9, when $w^a$ or $w^b$ is excited and transitions to 10a or 10b, an output wire is changed.  If any logic blocks are in case 9, its logic block cannot change excitations because Lemma 1 would be violated.  Thus far, we have shown using Lemma 1that the logic blocks in cases 1-9 cannot change excitations other than when drawn in the figure.  The last step is to show that the logic blocks in case 10a or 10b also cannot change excitations.  \\  
